%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Soham Dongargaonkar} % Your name
\address{sd4324@rit.edu \\ (585) 967-0514 \\  https://github.com/a3y3} % Your phone number and email
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Rochester Institute of Technology, Rochester, NY, USA} \hfill {\em Expected - December 2020} 
\\ Masters of Science in Computer Science
\\ Current GPA: 3.67
\\
\\{\bf Manipal Institute of Technology, Manipal, India             } \hfill {\em Earned - August 2018} 
\\ Bachelor of Technology in Information Technology
\end{rSection}

\begin{rSection}{Career Objective}
 Seeking a Software Development Internship. Available from May 2019.
\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Remembrall}
\hfill {\em Feb 2017 - April 2017} 
\begin{itemize}
    \itemsep0em 
  \item Created an Android App that helps you take notes and add reminders to keep yourself notified.
  \item Facilitated a quick, one touch account signup and login using Google+ SignIn API.
  \item Exploited Android APIs in Nougat (FirebaseJobDispatcher) in order to schedule notifications.
\end{itemize}
{\bf Beats}
\hfill {\em  Oct 2016 - Dec 2016} 
\begin{itemize}
  \item Developed an open source music web application that pulls local files and creates playlists.
  \item Used HTML5 audio to play music with PHP for backend.
  \item Developed a functionality that recommends songs based on frequency of listening to them.
\end{itemize}
{\bf Mechatron}
\hfill {\em Sept 2016 - Oct 2016}
\begin{itemize}
  \item Developed an online quiz system for TechTatva’16, MIT’s national technical fest.
  \item Designed the front-end and the back-end using JQuery and PHP. 
  \item Researched about common web attacks and devised mechanisms to protect the application against them.
\end{itemize}

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{0ex}} l }
Languages \ & Java, Go, Ruby on Rails, Jquery, PHP
 \\
Other &  Git, Postgresql, REST API, ActiveRecord, Sidekiq, JSON  \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{SJ Contracts, Pune}{June 2016}{Site Engineer}{}
\item On-site internship under this leading construction company. Learned and implemented various aspects such as quantity estimation, labour management and safety precautions.
\end{rSubsection}
\end{rSection}
\end{document}
