%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.50in,top=0.4in,right=0.50in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Sharelatex Example},
    bookmarks=true,
    pdfpagemode=FullScreen,
    }
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Soham Dongargaonkar} % Your name
\address{sd4324@rit.edu \\ (585) 967-0514 \\  https://github.com/a3y3} % Your phone number and email
\begin{document}

\begin{rSection}{Career Objective}
 Seeking a Software Development Internship. Available from May 2019.\\ 
 Interests: Web and App Development, Distributed Systems.
\end{rSection}

\begin{rSection}{Education}

{\bf Rochester Institute of Technology, Rochester, NY, USA} \hfill {\em Expected - December 2020} 
\\ Masters of Science in Computer Science
\\ Current GPA: 3.67
\\{\bf Manipal Institute of Technology, Manipal, India             } \hfill {\em Earned - August 2018} 
\\ Bachelor of Technology in Information Technology
\end{rSection}



\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{0ex}} l }
Languages \ & Java, Ruby on Rails, Go, PHP, JavaScript, jQuery, HTML, CSS
 \\
Other &  Git, PostgreSQL, REST API, ActiveRecord, Sidekiq, Android, JSON, SCSS, Bootstrap  \\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

    \begin{rSubsection}{Avalon Labs, Bangalore, India }{\em December 2017- July 2018}{Full Stack Intern}{}
    Developed and deployed LinkHero (\url{https://uselinkhero.com}), a marketing tool that enables users to track link clicks, earn affiliate revenue and promote their businesses.
    \item
    Programmed a link shortening system for link click tracking (Referrer Domain, IP Address, Geo-Location, etc.)
    \item 
    Designed a functionality to display custom "Call to Action" popups on a foreign URL by using iFrames.
    \item 
    Used Paypal API for payments, and later changed it to Stripe API, ensuring no data was lost through extensive testing.
    \item 
    Engineered an ability to refer LinkHero to a friend to earn direct money on the plan bought. 
    \item
    Deployed a Chrome Extension by adding custom REST-ful routes to allow quick link creation.\\
    Collaborated on Enkidu in a team of 4 and developed 2 other web apps.
    \end{rSubsection}
    
    \begin{rSubsection}{Clapoof Technologies, Manipal, India}{\em June 2017- July 2017}{Android UI Developer Intern}{}
    \item Designed and developed the UI/UX for the app using Material Design Guidelines in collaboration with a team of 3.
    \item Researched about usability testing and accessibility.
    \end{rSubsection}
    
    \begin{rSubsection}{Parikshit, Manipal, India}{\em September 2016 - December 2016}{Student Developer}{}
    \item Collaborated in a team of two to develop the official website for the student satellite program of Manipal University.
    \item Used git for version control and Bootstrap to design a mobile responsive, light weight website. 
    \end{rSubsection}
\end{rSection}

%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Remembrall}
\hfill {\em Feb 2017 - April 2017} 
\begin{itemize}
    \itemsep0em 
  \item Created an Android App that helps you take notes and add reminders to keep yourself notified.
  \item Facilitated a quick, one touch account signup and login using Google+ SignIn API.
  \item Exploited Android APIs in Nougat (FirebaseJobDispatcher) in order to schedule notifications.
\end{itemize}
{\bf Beats}
\hfill {\em  Oct 2016 - Dec 2016} 
\begin{itemize}
  \item Developed an open source music web application that pulls local files and creates playlists.
  \item Used HTML5 audio to play music with PHP for backend.
  \item Developed a functionality that recommends songs based on frequency of listening to them.
\end{itemize}
{\bf Mechatron}
\hfill {\em Sept 2016 - Oct 2016}
\begin{itemize}
  \item Developed an online quiz system for TechTatva’16, MIT’s national technical fest.
  \item Designed the front-end and the back-end using JQuery and PHP. 
  \item Researched about common web attacks and devised mechanisms to protect the application against them.
\end{itemize}

\end{rSection}
\end{document}
